Ancestry linkage in hybrid zones

### 2015-12-16 drafts/hybrid_zone.tex
added some simulation results

\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
\usepackage{natbib}
\usepackage{color}
% See the ``Article customise'' template for come common customisations
\newcommand{\alisa}[1]{{\em \color{red} #1}}

@@

\section{Introduction}
The process of speciation commonly involves allopatric divergence in relative isolation \cite{Coyne2004}. When formerly isolated populations come back into contact, a gradient of ancestry can form in geographic space, resulting in a hybrid zone \cite{Barton1985}. Throughout the genome, clines in ancestry may diminish over time due to migration; however, subsets of the genome that are experiencing selection may be expected to maintain clines in ancestry as selection against migrant, or hybrid, genotypes impedes gene flow across the hybrid zone \cite{Barton1979a}. The influence of selection on linked loci also prevents the mixing of ancestry at regions surrounding these loci, the effect of which diminishes with physical genomic distance \cite{Barton1986}.\\

@@

\subsection{Simulations}
Forward in time simulations were used to assess theoretical predictions. We simulate discrete demes with nearest-neighbor migration and non-overlapping generations. Each generation, an individual moves to a neighboring deme with probability $m$. The direction in which it moves is determined by a coin-flip, except at edge demes, where an individual moves in one direction with probability $m/2$. Following migration, the next generation is produced by replacing each individual in a deme by randomly choosing two parents with probability weighted by the fitness of their genotypes. The genotype of the new individual is generated by simulating a recombined chromosome from each parent. This simulation keeps track of the ancestry at each location in the chromosome for all individuals. Each individual has 1 pair of chromosomes of length 1 Morgan.

@@

Ancestry blocks were estimated using ChromopainterV2 \cite{Lawson2012}. \\

@@

\begin{table}
\begin{tabular}{l|c|c}
Individual ID \citep{Turner2014} & Population \citep{Turner2011} & Longitude(E)\\
\hline
FP112 & FS&11.665\\
FP67 & FS &11.665\\
FP114 & FS &11.665\\
FP79 & FS &11.665\\
FP152 &  FS &11.665\\
FP11 & GL &11.965\\
FP111&GL &11.965\\
FP59 & HA  &11.721\\
FP92 & HA &11.721\\
FP7 &  HA  & 11.721\\
FP45 & HA&11.721\\
FP244& HO &11.693\\
FP9&   RE&11.994\\
FP5 &  RF&11.767\\
FP78 &  SO &11.539\\
FP52 &  SO &11.539\\
FP180& SO &11.539\\
FP14 & ST&11.539\\
FP40 & ST&11.539\\
FP145 & TU&11.748\\
FP29&  TU&11.748\\
FP135& TU&11.748\\

\end{tabular}
\end{table}
\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
\usepackage{natbib}
\usepackage{color}
% See the ``Article customise'' template for come common customisations
\newcommand{\alisa}[1]{{\em \color{red} #1}}

@@

\section{Introduction}
The process of speciation commonly involves allopatric divergence in relative isolation \cite{Coyne2004}. When formerly isolated populations come back into contact, a gradient of ancestry can form in geographic space, resulting in a hybrid zone \citep{Barton1985}. Throughout the genome, clines in ancestry may diminish over time due to migration; however, subsets of the genome that are experiencing selection may be expected to maintain clines in ancestry as selection against migrant, or hybrid, genotypes impedes gene flow across the hybrid zone \citep{Barton1979a}. The influence of selection on linked loci also prevents the mixing of ancestry at regions surrounding these loci, the effect of which diminishes with physical genomic distance \citep{Barton1986}.\\

The mixing of ancestries is brought about by the the process of recombination that takes place every generation. The expected distribution of lengths of unbroken ancestry have been previously described under neutral conditions \cite[e.g.][]{Gravel2012,Sedghifar2015}. Here we investigate expected genome-wide patterns of co-ancestry in the presence of selection. Selection against migrant ancestries is expected to reduce admixture proportions at and surrounding a target of selection. The effect on patterns of ancestral block lengths is, however, less well understood. Because of rapid removal from the population, we expect to observe few short blocks of foreign ancestry surrounding the selected locus, with this effect becoming more pronounced further away from the center of a hybrid zone.\\

@@

\subsection{Simulations}
Forward in time simulations were used to assess theoretical predictions. We simulate discrete demes with nearest-neighbor migration and non-overlapping generations. Each generation, the dispersal distance of an individual is sampled from a normal distribution, and then discretized to correspond to a deme that is a corresponding distance away. Following migration, the next generation is produced by replacing each individual in a deme by randomly choosing two parents with probability weighted by the fitness of their genotypes. The genotype of the new individual is generated by simulating a recombined chromosome from each parent. This simulation keeps track of the ancestry at each location in the chromosome for all individuals. Each individual has 1 pair of chromosomes of length 1 Morgan. We simulate a single selected locus at position 1M along the chromosome.

Hybrid zones of ages 10, 100 and 1000 generations were simulated under conditions of $\sigma=1$ and $s=0.1$. From this we measure unbroken tract lengths to the right of the selected locus. These were compared to the output of neutral simulations with $s=0$

@@

Ancestry blocks were estimated using ChromopainterV2 \cite{Lawson2012} and STRUCTUREv2 \cite{Falush2003} with $k=2$.\\

@@

\begin{table}
\begin{tabular}{l|c|c}
Individual ID  & Population \citep{Turner2011} & Longitude(E)\\
\citep{Turner2014}& \citep{Turner2011}&\\
\hline
FP112 & FS&11.665\\
FP67 & FS &11.665\\
FP114 & FS &11.665\\
FP79 & FS &11.665\\
FP152 &  FS &11.665\\
FP11 & GL &11.965\\
FP111&GL &11.965\\
FP59 & HA  &11.721\\
FP92 & HA &11.721\\
FP7 &  HA  & 11.721\\
FP45 & HA&11.721\\
FP244& HO &11.693\\
FP9&   RE&11.994\\
FP5 &  RF&11.767\\
FP78 &  SO &11.539\\
FP52 &  SO &11.539\\
FP180& SO &11.539\\
FP14 & ST&11.539\\
FP40 & ST&11.539\\
FP145 & TU&11.748\\
FP29&  TU&11.748\\
FP135& TU&11.748\\

\end{tabular}
\end{table}

\section{Discussion}
Topics include\\
- ignoring coalescent\\
- single locus model, selection is STRONG

\bibliographystyle{dinat}
\bibliography{library}

\end{document}
